The Ultraviolet Environment of a Tropical Megacity in Transition: Mexico City 2000-2019

### 2021-07-21 Paper/v2/Article_UV_Mexico.tex
Rename paper folders

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional packages needed here.  Only include packages
%% which are essential, to avoid problems later.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{chemformula} % Formula subscripts using \ch{}
\usepackage[T1]{fontenc} % Use modern font encodings
\usepackage{lineno}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\usepackage{multirow}
\usepackage{achemso}
\setkeys{acs}{etalmode=truncate,maxauthors=40}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% If issues arise when submitting your manuscript, you may want to
%% un-comment the next line.  This provides information on the
%% version of every file you have used.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%\listfiles

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[The UV Radiation in Mexico City]
  {The Ultraviolet Radiation Environment of a Tropical Megacity in Transition: Mexico
  City 2000-2019}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The abstract environment will automatically gobble the contents
%% if an abstract is not used by the target journal.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  Tropical regions experience naturally high levels of UV radiation, but
  urban pollution can reduce these levels substantially. We analyzed 20
  years of measurements of the UV Index (UVI) at several ground-level
  locations in the Mexico City Metropolitan Area and compared these data
  with UVI values derived from satellite observations of ozone
  and clouds (but not local pollution). The ground-based measurements were
  systematically lower than the satellite-based estimates, by ca. 40\% in
  2000 and 25\% in 2019. Calculations with a radiative transfer model and
  observed concentrations of air pollutants explained well the difference
  between satellite and ground-based UVI, and showed specific contributions
  from aerosols, O\textsubscript{3}, NO\textsubscript{2},
  and SO\textsubscript{2}, in decreasing order of importance. Such large
  changes in UV radiation between 2000 and 2019 have important implications
  ranging from human health (skin cancer and cataract induction) to air
  pollution control (photochemical smog formation).
\end{abstract}

@@

The question of how air pollution alters the urban UV radiation environment
(and~\emph{vice versa}) is not new, but studies have relied mostly on
numerical models \cite{Liu_1991,Sabziparvar_1998,Madronich_2011},
with relatively few available observations (e.g.,
\citet{McKenzie_2008}, \citet{Panicker_2009}, \citet{Palancar_2013},
reviewed by \citet{Bais_2015}). Increases in UV have been estimated as a consequence
of emission reductions over the last decades, e.g. in China,\citep{Hollaway_2019,Li_2018,Wang_2020}
and have led to less-than-expected
reductions in photochemical smog, in part due to stronger UV
photochemistry.\citep{Wang_2019,Gao_2020,Ma_2021}
Emission reductions have also occurred
globally during the 2020 COVID-19 pandemic,\citep{Bauwens_2020,Venter_2020}
but ground-level ozone in some polluted areas has actually
increased,\citep{Shi_2020,Le_2020} due at least in part to the increased UV
radiation. Unfortunately, the observational data base of relevant UV
radiation remains rather sparse to evaluate such model-predicted feedbacks between chemistry and radiation.~~

The environment of Mexico City is of particular interest for several
reasons: (1) Nearly 23 million people inhabit the Mexico City
Metropolitan Area (MCMA), and the UV radiation environment has direct implications
for their health, both in terms of skin/eye UV exposure and~\emph{via}
photochemical smog formation. (2) As a tropical megacity, it is to some
extent representative of the situation of many others, with year-round
intense midday UV irradiance, a shallower atmosphere due to the city's
high elevation of 2240 m above sea level, and a transition toward newer
and cleaner technologies, leading to gradual improvements in air
quality. (3) Air quality within MCMA has undergone extensive scrutiny,
with a well-established monitoring network operating since
1986,\cite{RAMA}
numerous intensive field campaigns to study the
meteorology, emissions, and photochemistry of smog
formation,\citep{Doran_1998,Molina_2007,Molina_2010}
and numerical modeling incorporating the
evolving knowledge.\citep{Jazcilevich_2005,Tie_2007,Zhang_2009,Zavala_2020}
This extensive body of knowledge
provides the foundation for understanding our study.

In this work, we analyze two decades of continuous measurements of the UV Index
at multiple locations within the MCMA, collected by the Secretariat of
the Environment (Secretaría del Medio Ambiente,
SEDEMA)\footnote{\url{https://www.sedema.cdmx.gob.mx/}} of the Mexico
City government as part of an intensive monitoring network over the
MCMA. The UV Index is defined as:

@@

The UVI is recognized by the World Health and Meteorological
Organizations (WHO and WMO) as a standardized index of UV
radiation\cite{who2002} for global public information. An advantage
of using the UVI as (one) measure of UV radiation is that it is being
increasingly observed or calculated and disseminated, enabling more
objective comparisons among seasons and locations. The UVI observations
from Mexico City, considered here, are an important element of this
global picture.

@@

The Mexico City Metropolitan Area is located at 19.4°N, 99.1°W and 2240
meters above sea level (m asl), surrounded by mountain ridges exceeding
5000 m asl, with complex topography and thermal inversions that inhibit
winds and favor intense air pollution.\citep{Whiteman_2000,Fast_2007,Carre_n_Sierra_2015}
Air quality
monitoring and surface meteorological measurements in the MCMA are
conducted continuously by the Automated Atmospheric Monitoring Network
(RAMA, by its Spanish acronym) of the Atmospheric Monitoring System
(SIMAT, by its Spanish acronym) of the Mexico City government. Since the
year 2000, UV radiometers (model 501-A, Solar Light Company Inc.,
Glenside, PA) detecting wavelengths between 280-400 nm have been
measuring erythemally-weighted solar radiation. Calibration of the
UV sensors has been carried out annually by comparing against a
factory-calibrated reference sensor. The output voltages from the
network’s sensors have been compared for at least one week against the UV
readings from the reference sensor to derive new calibration factors, which typically differed
from the old ones by 2\% or less.
Reference sensors were also calibrated by the manufacturer and updated
periodically (between 3 to 5 years) to reduce systematic errors due to drifts in sensitivity.
Long term calibration drifts are minimized by these yearly re-calibrations.
Although at the beginning only a few stations were in operation and
varied, currently 11 stations are recording erythemal
irradiances, which are then multiplied by 40 (see
Eq.~{\ref{eq:UVI}}) to give UV Indices.
Table~{\ref{table:stations}} describes the location of
the stations where the UV Index has been measured.
Figure~{\ref{fig:map}} shows how the radiometers of the
SIMAT have been distributed over MCMA, prioritizing sites with higher population density.
Near real-time data for each station are
available on the SIMAT official
website~\url{http://www.aire.cdmx.gob.mx/default.php}. Daily maximum
values (\(UVI_{\max}\)) were extracted~in each of the stations
around solar noon from the time interval from 11:00 h-15:00 h CST
(Central Standard Time). This database~with 7305 continuous days of
measurements during the period 2000-2019 was analyzed.

\begin{table}[H]
  \centering
  \begin{tabular}{ccccc}
    \hline
    Station  & Environment     & Lat (°N) & Lon (°W) & El (m asl) \\ \hline
    CHO      & semi-urban      & 19.27    & 98.89    & 2253       \\
    CUT      & ecological park & 19.72    & 99.20    & 2263       \\
    FAC      & urban           & 19.48    & 99.24    & 2299       \\
    HAN      & urban           & 19.42    & 99.08    & 2235       \\
    LAA      & urban           & 19.48    & 99.15    & 2255       \\
    MER      & downtown        & 19.42    & 99.12    & 2245       \\
    MON      & rural           & 19.46    & 98.90    & 2252       \\
    MPA      & rural           & 19.18    & 98.99    & 2594       \\
    PED      & residential     & 19.33    & 99.20    & 2326       \\
    SAG      & urban           & 19.53    & 99.03    & 2241       \\
    SFE      & residential     & 19.36    & 99.26    & 2599       \\
    TLA      & urban           & 19.53    & 99.20    & 2311       \\
    UNAM$^*$ & University city & 19.33    & 99.18    & 2294       \\\hline
  \end{tabular}
  \caption{{{{SIMAT stations and AERONET site$^*$, environmental descriptors and geographical
                positions. Abbreviations names: Chalco (CHA), Cuautitlán (CUT), FES Acatlán
                (FAC), Hangares (HAN), Laboratorio de Análisis Ambiental (LAA), Merced
                (MER), Montecillo (MON), Milpa Alta (MPA), Pedregal (PED), San Agustín
                (SAG), Santa Fe (SFE), Tlalnepantla (TLA) and National Autonomous University of Mexico (UNAM$^*$)}}}}
  \label{table:stations}
\end{table}

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=0.70\columnwidth]{figures/map}
    \caption{{Map with the location of the SIMAT continuous monitoring stations over
          MCMA. Sites denoted by the blue solid dots correspond to SIMAT stations
          with UV measurements, while the black dots indicate SIMAT stations
          without UV measurements, the site indicated by an open blue dot represents a
          discontinued site, the red dot shows the location of the
          AERONET site. The location~of Mexico City and the acronyms of the UV and
          AERONET site are shown at the upper and lower frames at the right
          respectively.
            {\label{fig:map}}%
        }}
  \end{center}
\end{figure}

To explore the relationship between UVI and air pollutants
levels, the hourly averages for ozone (O\textsubscript{3}), carbon
monoxide (CO), nitrogen dioxide (NO\textsubscript{2}), sulfur
dioxide~(SO\textsubscript{2}) and particle matter with diameter
sizes~\(\le\) 10 ~$\mu$m (PM\textsubscript{10}), were downloaded
from the SIMAT.\cite{pollutants_data} For purposes of assessing the
influence on the UV Index at solar noon, only values obtained between
11h and 15h CST were considered for the trends analysis. Pollutant
measurements are conducted by the SIMAT using regulatory-grade
commercial instruments. Measurement principles include ultraviolet
photometry (model 400E, Teledyne-API) for O\textsubscript{3},
chemiluminescence (model 200E, Teledyne-API) for NO\textsubscript{2}, UV
fluorescence (model 100E, Teledyne API) for SO\textsubscript{2}, and
infrared absorption (model 300E, Teledyne-API) for CO. The
PM\textsubscript{10} continuous mass concentration was measured with
Tapered Element Oscillating Microbalance (TEOM 1400AB or TEOM 1405 DF,
Thermo Scientific) monitors. Gaseous pollutant levels are reported in
ppb concentration units for O\textsubscript{3}, SO\textsubscript{2} and
NO\textsubscript{2}, and in ppm for CO. Particulate matter mass
concentration is reported in $\mu$g m\textsuperscript{-3} at local
temperature and pressure.

Aerosol optical depth at 340 nm was obtained from the Institute of
Geophysics of the National Autonomous University of Mexico (UNAM).
Measurements were conducted with a CIMEL sun photometer model CE-318,
which is an automatic sun-sky-scanning spectral radiometer of
the AErosol RObotic NETwork (AERONET~\citep{Holben_1998}). The data
Product Level 2.0 and 1.5 (only in 2019) were selected, and annual
averages AOD\textsubscript{340} were calculated for the period 2000-2019,
except for the year 2011 which contained large data gaps and was therefore not used.
A previous study of the AOD behavior from 2000 to 2014 demonstrated that data gaps did not
significantly change the trends calculated for this.\citep{Carabali_2017}
Only 8\% of the data between the years 2014 and 2019 were missing.
The largest data gap occurred in 2018 when the instrument was returned for calibration.

@@

The UV Index data derived from satellite-based measurements
were used for comparison with the ground-based measurements.
These data were provided by the Ozone Monitoring
Instrument (OMI)~on board of AURA-NASA satellite.\citep{dcio} OMI
is operated collaboratively by the Netherlands Agency for Aerospace
Programmes (NIVR), the Finnish Meteorological Institute (FMI) and NASA.
OMI performs observations over a geographical area of 13$\times$24km\textsuperscript{2} at nadir. For
the coordinates (19.33°N, 99.18°W) and elevation (2268 m asl) of Mexico City,
the satellite overpass time is between 19:00h - 21:00h UTC (20:00h - 22:00h CET).
The OMI instrument measures reflected and backscattered radiances of the atmosphere-surface system at several UV wavelengths.\cite{Tanskanen_2006} The ozone column is estimated by differential absorption of several adjacent
wavelengths in the O\textsubscript{3} Huggins band\citep{Veefkind_2006}, and is used in a radiative transfer model to estimate clear-sky UVI at the surface. Clouds are estimated from the observed reflectivity at a wavelength not affected by O\textsubscript{3} absorption (360 nm) and the clear-sky UVI is adjusted for their presence.\cite{Tanskanen_2007} A correction for absorbing aerosols is made using a global aerosol climatology.\citep{Arola_2009}
The UV Index used for Mexico City corresponds to values at local noon time and clear sky
from OMUVB Level 2 OVP data product, version 1.3 and collection 3.

@@

Calculations of the UV Index were also made with the Tropospheric
Ultraviolet Visible (TUV v5.3) model.\citep{Madronich_1987} The
model atmosphere is represented by 80 vertical layers, each 1 km thick,
starting at the 2.24 km asl elevation of MCMA, and for which the first
three km constitute the atmospheric boundary layer
(BL).\citep{Shaw_2007} The ozone profile above the BL is from the US
Standard Atmosphere, but rescaled to a value of 259.6 DU. Total ozone columns
including the BL contributions (of 13.7 DU in the year 2000 and 9.8 DU
in 2019, see below) were 273.1 DU in 2000 and 269.2 DU in 2019, respectively. The
climatological O\textsubscript{3} column for this latitude and season is
about 270 DU (plus or minus ca. 5 DU) so in good agreement with the
values used here.

@@

Above the atmospheric boundary layer, the model atmosphere was specified to be free of aerosols,
NO\textsubscript{2}, or SO\textsubscript{2}. In one
sensitivity study, a total AOD of 0.7 was redistributed placing 0.2 in
the free troposphere (decreasing vertically with an exponential scale
height of 4 km, and 0.5 remaining in the BL). The calculated UVI
differed by less than 1\%. Thus, as long as the total AOD is known,
knowledge of the exact vertical aerosol profile is not critical for
ground-level UVI, though it would obviously affect the vertical structure of
photolysis frequencies.

@@

Figure~{\ref{628947}} shows the diurnal variation of
the UVI for typical cloud-free days, for different seasons and
several locations (CHO, MER, MON, PED, SAG, SFE and TLA).
The selection of cloud-free days was aided by comparison of the measurements
with the TUV model predictions for clear skies, with prolonged deviations and
fluctuations usually indicative of cloudy conditions. However,
during the rainy period (from June to October) at least a brief episode of clouds,
is seen at CHO station around noon on 23 June
2017. Peak values range from 8 during autumn/winter to above 12
in spring/summer, in correspondence to the respective December and June
solstices. Although the stations are all within a 25 km radius,
substantial differences among them are notable. Survey of the locations
revealed that shadowing from nearby structures is not an issue. The good
agreement in the morning, followed by more divergence in the afternoon,
is consistent with the development of photo-chemical pollution hotspots
during the day. Previous studies (e.g., \citet{Castro_2001} and
\citet{Palancar_2013}) have shown
that surface UV radiation in Mexico City is attenuated significantly by
aerosols. The measurements shown in Fig.~{\ref{628947}}
are consistent with this increasing pollution during the course of the
day, with highest aerosol loading (and highest variability) attained in
the afternoon. Further support for the role of pollution in suppressing
the UVI comes from the observation made at the Santa Fe (SFE) site which
in Fig.~{\ref{628947}} are seen to be systematically
higher, e.g. by over 10\% in autumn afternoons, compared to the other
stations. The SFE station is displaced to the west from the majority of
the other stations, and remains in the outskirts. This site is also
approximately 300 m higher than Mexico City downtown, so that the cleaner atmosphere at SFE
is a result of the station’s location farther away from pollution sources,
both horizontally and vertically.\citep{SEDEMA2018a} It is indeed expected to have
higher values of the UVI, in agreement with the observations.

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=0.70\columnwidth]{figures/season}
    \caption{{UV Index measurements at 1-minute resolution from several SIMAT stations within the MCMA
          under mostly cloudless conditions for representative days of the year.
            {\label{628947}}%
        }}
  \end{center}
\end{figure}

The daily maximum UV Index values of each station,~\(UVI_{\max}\),
are summarized in Figure~{\ref{461017}} for the entire period 2000-2019.
These values are seen to range
from 1 to 16, with a majority (61\%) of the days
experiencing~\(UVI_{\max}\) values between 6 and 10, and remarkably
few, less than 1\%, in the 13-16 range.~The lowest values are
likely due to winter days with heavy cloud cover and low sun angles, and
UV attenuation by pollutants could also be amplified under such
conditions, due to longer photon path lengths at low sun and within
clouds. The extreme sparsity of high UVI values remains surprising, and
may be an indication of the rarity of extremely unpolluted days within
the city.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional packages needed here.  Only include packages
%% which are essential, to avoid problems later.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{chemformula} % Formula subscripts using \ch{}
\usepackage[T1]{fontenc} % Use modern font encodings
\usepackage{lineno}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\usepackage{multirow}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% If issues arise when submitting your manuscript, you may want to
%% un-comment the next line.  This provides information on the
%% version of every file you have used.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%\listfiles

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[The Ultraviolet Environment]
  {The Ultraviolet Environment of a Tropical Megacity in Transition: Mexico
  City 2000-2019}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The abstract environment will automatically gobble the contents
%% if an abstract is not used by the target journal.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  Tropical regions experience naturally high levels of UV radiation, but
  urban pollution can reduce these levels substantially. We analyzed 20
  years of measurements of the UV Index (UVI) at several ground-level
  locations in the Mexico City Metropolitan Area and compared these with
  UVI values estimated from satellite overpasses observing ozone and
  clouds (but not local pollution). The ground-based measurements were
  systematically lower than the satellite-based estimates, by ca. 40\% in
  2000 and 20\% in 2019. Calculations with a radiative transfer model and
  observed concentrations of air pollutants explained well the difference
  between satellite- and ground-based UVI, and showed specific
  contributions from boundary layer and free trophosperic aerosols,
  O\textsubscript{3}, NO\textsubscript{2}, and SO\textsubscript{2}, in
  decreasing order of importance. Such large changes in UV radiation
  between 2000 and 2019 have important implications ranging from human
  health (skin cancer and cataract induction) to air pollution control
  (photochemical smog formation).
\end{abstract}

@@

The question of how air pollution alters the urban UV environment
(and~\emph{vice versa}) is not new, but studies have relied mostly on
numerical models \cite{Liu_1991,Sabziparvar_1998,Madronich_2011},
with relatively fewer available observations (e.g.,
\citet{McKenzie_2008}, \citet{Panicker_2009}, \citet{Palancar_2013},
reviewed by \citet{Bais_2015}). Increases in UV have been
estimated in association with decadal emission reductions, e.g. in
China,\citep{Hollaway_2019,Li_2018,Wang_2020}
and that have led to less-than-expected
reductions in photochemical smog, in part due to stronger UV
photochemistry.\citep{Wang_2019,Gao_2020,Ma_2020}
Emission reductions have also occurred
globally during the 2020 COVID-19 pandemic,\citep{Bauwens_2020,Venter_2020}
but ground-level ozone in some polluted areas has actually
increased,\citep{Shi_2020,Le_2020} due at least in part to the increased UV
radiation. Unfortunately, the observational data base of relevant UV
radiation remains rather sparse to evaluate such model-derived
hypotheses.~~

The environment of Mexico City is of particular interest for several
reasons: (1) Nearly 23 million people inhabit the Mexico City
Metropolitan Area (MCMA), and the UV environment has direct implications
for their health, both in terms of skin/eye UV exposure and~\emph{via}
photochemical smog formation. (2) As a tropical megacity, it is to some
extent representative of the situation of many others, with year-round
intense midday UV irradiance, a shallower atmosphere due to the city's
high elevation of 2240 m above sea level, and a transition toward newer
and cleaner technologies, leading to gradual improvements in air
quality. (3) Air quality within MCMA has undergone extensive scrutiny,
with a well-established monitoring network since
1986,\cite{RAMA}
numerous intensive field campaigns to study the
meteorology, emissions, and photochemistry of smog
formation,\citep{Doran_1998,Molina_2007,Molina_2010}
and numerical modeling incorporating the
evolving knowledge.\citep{Jazcilevich_2005,Tie_2007,Zhang_2009,Zavala_2020}
This extensive body of knowledge
provides the foundation for understanding our study.

Here, we analyze two decades of continuous measurements of the UV Index
at multiple locations within the MCMA, collected by the Secretariat of
the Environment (Secretaría del Medio Ambiente,
SEDEMA)\footnote{\url{https://www.sedema.cdmx.gob.mx/}} of the Mexico
City government as part of an intensive monitoring network over the
MCMA. The UV Index is defined as:

@@

The UVI is recognized by the World Health and Meteorological
Organizations (WHO and WMO) as a standardized metric of UV
radiation\cite{who2002} for global public information. An advantage
of using the UVI as (one) metric of UV radiation is that it is being
increasingly observed or calculated and disseminated, enabling more
objective comparisons among seasons and locations. The UVI observations
from Mexico City, considered here, are an important element of this
global picture.

@@

The Mexico City Metropolitan Area is located at 19.4°N, 99.1°W, 2240
meters above sea level (asl), surrounded by mountain ridges exceeding
5000 m asl, with complex topography and thermal inversions that inhibit
winds and favor intense air pollution.\citep{Whiteman_2000,Fast_2007,Carre_n_Sierra_2015}
Air quality
monitoring and surface meteorological measurements in the MCMA are
conducted continuously by the Automated Atmospheric Monitoring Network
(RAMA, by its Spanish acronym) of the Atmospheric Monitoring System
(SIMAT, by its Spanish acronym) of the Mexico City government. Since the
year 2000, UV radiometers (model 501-A, Solar Light Company Inc.,
Glenside, PA) detecting wavelengths between 280-400 nm have been
measuring erythemally-weighted solar radiation. The calibration of the
UV sensors was carried out annually by comparing against a
factory-calibrated reference sensor. The output voltages from the
measuring sensors were compared during at least one week against the UV
readings from the reference sensor to derive the calibration factor. New
calibration factors typically differed from the old ones by 2\% or less.
Reference sensors were also calibrated by the manufacturer and updated
periodically (between 3 to 5 years) to avoid any bias due to aging. Long
term calibration drift was avoided by the yearly re-calibrations.
Although at the beginning only a few stations were in operation and have
been changing, currently 11 stations are recording erythemal
irradiances, which are then multiplied by 40 (see
Eq.~{\ref{eq:UVI}}) to give UV Indices.
Table~{\ref{table:stations}} describes the location of
the stations where UV Index has been measured.
Figure~{\ref{fig:map}} shows how the radiometers of the
SIMAT have been distributed over MCMA, prioritizing the sites with more
density of population. Near real-time data for each station are
available on the SIMAT official
website~\url{http://www.aire.cdmx.gob.mx/default.php}. Daily maximum
values (\(UVI_{\max}\)) were extracted~from each of the stations
around solar noon from the time interval from 11:00 h-15:00 h CST
(Central Standard Time). This database~with 7305 continuous days of
measurements during the period 2000-2019 was analyzed.

\begin{table}[H]
  \centering
  \begin{tabular}{ccccc}
    \hline
    Station  & Environment     & Lat (ºN) & Lon (ºW) & El (masl) \\ \hline
    CHO      & semi-urban      & 19.27    & 98.89    & 2253      \\
    CUT      & ecological park & 19.72    & 99.20    & 2263      \\
    FAC      & urban           & 19.48    & 99.24    & 2299      \\
    HAN      & urban           & 19.42    & 99.08    & 2235      \\
    LAA      & urban           & 19.48    & 99.15    & 2255      \\
    MER      & downtown        & 19.42    & 99.12    & 2245      \\
    MON      & rural           & 19.46    & 98.90    & 2252      \\
    MPA      & rural           & 19.18    & 98.99    & 2594      \\
    PED      & residential     & 19.33    & 99.20    & 2326      \\
    SAG      & urban           & 19.53    & 99.03    & 2241      \\
    SFE      & residential     & 19.36    & 99.26    & 2599      \\
    TLA      & urban           & 19.53    & 99.20    & 2311      \\
    UNAM$^*$ & University city & 19.33    & 99.18    & 2294      \\\hline
  \end{tabular}
  \caption{{{{SIMAT stations and AERONET site$^*$, environmental descriptors and geographical
                positions. Abbreviations names: Chalco (CHA), Cuautitlán (CUT), FES Acatlán
                (FAC), Hangares (HAN), Laboratorio de Análisis Ambiental (LAA), Merced
                (MER), Montecillo (MON), Milpa Alta (MPA), Pedregal (PED), San Agustín
                (SAG), Santa Fe (SFE), Tlalnepantla (TLA) and National Autonomous University of Mexico (UNAM$^*$)}}}}
  \label{table:stations}
\end{table}

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=0.70\columnwidth]{figures/map}
    \caption{{Map with the location of the SIMAT continuous monitoring stations over
          MCMA. Sites denoted by the blue solid dots correspond to SIMAT stations
          with UV measurements, while the black dots indicate SIMAT stations
          without UV measurements, the site on open blue dot represents a
          discontinued site, the red dot corresponds to the location of the
          AERONET site. The location~of Mexico City and the acronyms of the UV and
          AERONET site are shown at the upper and lower frames at the right
          respectively.
            {\label{fig:map}}%
        }}
  \end{center}
\end{figure}

With the aim to explore the relationship between UVI and air pollutants
levels, the hourly averages for ozone (O\textsubscript{3}), carbon
monoxide (CO), nitrogen dioxide (NO\textsubscript{2}), sulfur
dioxide~(SO\textsubscript{2}) and particle matter with diameter
sizes~\(\le\) 10 ~$\mu$m (PM\textsubscript{10}), were downloaded
from the SIMAT.\cite{atmosfrico} For purposes of assessing the
influence on the UV Index at solar noon, only values obtained between
11h and 15h CST were considered for the trends analysis. Pollutant
measurements are conducted by the SIMAT using regulatory-grade
commercial instruments. Measurement principles include ultraviolet
photometry (model 400E, Teledyne-API) for O\textsubscript{3},
chemiluminescence (model 200E, Teledyne-API) for NO\textsubscript{2}, UV
fluorescence (model 100E, Teledyne API) for SO\textsubscript{2}, and
infrared absorption (model 300E, Teledyne-API) for CO. The
PM\textsubscript{10} continuous mass concentration was measured with
Tapered Element Oscillating Microbalance (TEOM 1400AB or TEOM 1405 DF,
Thermo Scientific) monitors. Gaseous pollutant levels are reported in
ppb concentration units for O\textsubscript{3}, SO\textsubscript{2} and
NO\textsubscript{2}, and in ppm for CO. Particulate matter mass
concentration is reported in $\mu$g m\textsuperscript{-3} at local
conditions for temperature and pressure.

Aerosol optical depth at 340 nm was obtained from the Institute of
Geophysics of the National Autonomous University of Mexico (UNAM);
measurements were conducted with a CIMEL sun photometer model CE-318,
which is an automatic sun-sky-scanning spectral radiometer of
the AErosol RObotic NETwork (AERONET~\citep{Holben_1998}). The data
Product Level 2.0 and 1.5 (only in 2019) were selected, and annual
averages AOD\textsubscript{340} were calculated from continuous
measurements during at least 7 months. A previous study of the AOD
behavior from 2000 to 2014 demonstrated that the gaps of data did not
significantly change the trends over the analyzed
period.\citep{Carabali_2017} From 2014 to 2019 there was only 8\% of the
missing data, when the instrument was sent for calibration in 2018.

@@

Estimates of the UV Index from satellite-based measurements of clouds
and O\textsubscript{3} were used for comparing to the ground-based
measurements. These data were provided by the Ozone Monitoring
Instrument (OMI)~on board of AURA-NASA satellite.\citep{dcio} OMI
was created in cooperation between the Netherlands Agency for Aerospace
Programmes (NIVR), the Finnish Meteorological Institute (FMI) and NASA.
OMI (hereafter OMI-Aura/NIVR-FMI-NASA) performs observations over a
geographical dimension of 13$\times$24km\textsuperscript{2} at nadir. For
Mexico City, the satellite overpass time is between 19:00h - 21:00h UTC
and data are specific for the coordinates and elevation of Mexico City.
Measurements of the ozone profile and cloud cover are used via a
radiative transfer model to estimate the UVI at the ground. The OMI web
site reports UVI values for both the overpass time, and corrected to
local solar noon.

While the early OMI estimates of the UVI did not consider aerosols in
the boundary layer, \citet{Arola_2009} suggested correcting
the clean-skies UV index with a reduction factor based on a monthly
global climatology of BL aerosols. For Mexico City a reduction of about
8\% is applied, starting ca. 2013, to the OMI UVI data.

@@

Calculations of the UV Index were also made with the Tropospheric
Ultraviolet Visible (TUV v5.3) model.\citep{Madronich_1987} The
model atmosphere was represented by 80 vertical layers, each 1 km thick,
starting at the 2.24 km asl elevation of MCMA, and for which the first
three km constitute the atmospheric boundary layer
(BL).\citep{Shaw_2007} The ozone profile above the BL is from the US
Standard Atmosphere, but rescaled to a value of 259.6 DU. Totals
including the BL contributions (of 13.7 DU in the year 2000 and 9.8 DU
in 2019, see below) were 273.1 DU in 2000 and 269.2 DU. The
climatological O\textsubscript{3} column for this latitude and season is
about 270 DU (plus or minus ca. 5 DU) so in good agreement with the
values used here.

@@

Above the atmospheric boundary layer, the model was taken to be free of
aerosols, NO\textsubscript{2}, or SO\textsubscript{2}. In one
sensitivity study, a total AOD of 0.7 was redistributed placing 0.2 in
the free troposphere (decreasing vertically with an exponential scale
height of 4 km, and 0.5 remaining in the BL). The calculated UVI
differed by less than 1\%. Thus, as long as the total AOD is known,
knowledge of the exact vertical aerosol profile is not critical towards
ground-level UVI -- but would obviously affect the vertical structure of
photolysis frequencies.

@@

Figure~{\ref{628947}} shows the diurnal variation of
the UVI for several specific cloud-free days, for different seasons and
several locations (CHO, MER, MON, PED, SAG, SFE and TLA). UV Index from
TUV model was used as reference of the behavior under clear sky days.
According to the comparison of measurements minute by minute, the dates
with prolonged fluctuations along the day were discarded. However,
during the rainy period (from June to October) at least a brief clouds
presence is common, as shown at CHO station around noon in 13 June
2017. Peak values range from 8 during autumn/winter to above 12
in spring/summer, in correspondence to the respective December and June
solstices. Although the stations are all within a 25 km radius,
substantial differences among them are notable. Survey of the locations
revealed that shadowing from nearby structures is not an issue. The good
agreement in the morning, followed by more divergence in the afternoon,
is consistent with the development of photo-chemical pollution hotspots
during the day. Previous studies (e.g., \citet{Castro_2001} and
\citet{Palancar_2013}) have shown
that surface UV radiation in Mexico City is attenuated significantly by
aerosols. The measurements shown in Fig.~{\ref{628947}}
are consistent with this increasing pollution during the course of the
day, with highest aerosol loading (and highest variability) attained in
the afternoon. Further support for the role of pollution in suppressing
the UVI comes from the observation made at the Santa Fe (SFE) site which
in Fig.~{\ref{628947}} are seen to be systematically
higher, e.g. by over 10\% in autumn afternoons, compared to the other
stations. The SFE station is displaced to the west from the majority of
the other stations, and remains in the outskirts. This site is also
approximately 300 m higher than Mexico City downtown, so that the
cleaner atmosphere results from both vertical and horizontal variations
in pollution levels.\citep{SEDEMA2018a} It is indeed expected to have
higher values of the UVI, in agreement with the observations.

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=0.70\columnwidth]{figures/season}
    \caption{{UV Index measured over MCMA by SIMAT stations each minute along the day
          under practically cloudless conditions for representative days of the
          year.
            {\label{628947}}%
        }}
  \end{center}
\end{figure}

The daily maximum UV Index of each station is denoted
by~\(UVI_{\max}\), all of them were counted in the period 2000-2019.
As shown in Figure~{\ref{461017}}, these values ranged
from 1 to 16, with a majority (61\%) of the days
experienced~\(UVI_{\max}\) values between 6 and 10, and remarkably
few, less than 1\%, in the higher 13-16 range.~The lowest values are
likely due to winter days with heavy cloud cover and low sun angles, and
UV attenuation by pollutants could also be amplified under such
conditions, due to longer photon path lengths at low sun and within
clouds. The extreme sparsity of high UVI values remains surprising, and
may be an indication of the rarity of extremely unpolluted days within
the city.

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=0.49\columnwidth]{figures/Histogram}
    \caption{{Frequency distribution of daily maximums UV Index values in Mexico City
    during 2000 -2019.
    {\label{461017}}%
    }}
  \end{center}
\end{figure}
